Rotations and Insecticide Resistance initial plots

### 2017-10-05 inst/documents/rotations1.Rmd
build doc

---
title: "Rotations and Insecticide Resistance"
output:
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex

@@

```{r,echo=FALSE,results='hide',warning=FALSE}
  library(rotations)
  library(ggplot2)
```

### Rotation interval 50 generations, migration 0.01, steps through insecticides

```{r Fig1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=7.5, fig.width=7.5, fig.show='hold', fig.align='left', fig.cap="Figure 1"}

@@

### decreasing migration to 0.001

```{r Fig1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=7.5, fig.width=7.5, fig.show='hold', fig.align='left', fig.cap="Figure 1"}

@@

@@

```{r Fig1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=7.5, fig.width=7.5, fig.show='hold', fig.align='left', fig.cap="Figure 1"}

>>>>

---
title: "Rotations and Insecticide Resistance initial plots"
output:
  pdf_document:
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex

@@

```{r, eval=TRUE, include=FALSE}

library(knitr)
opts_chunk$set(fig.height=7, fig.width=7)
# opts_chunk$set(dev="tiff",
#                dev.args=list(compression="lzw"),
#                dpi=300,
#                cache=FALSE,
#                fig.path='pap2figs/')
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Rotation interval 50, migration 0.01"}

# Interval 50, migration 0.01

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Rotation interval 50, migration 0.001"}

# Decrease migration to 0.001

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Rotate when resistant, migration 0.001"}

@@
